### 2021-03-10 Organismal_paper/Organismal_supplement.Rmd
repo uptodate
started post review process at IOB

![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/tentillaPresenceSIM.png)

@@

![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoaband phenotype presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)

@@

![\label{specimens} Specimen catalog. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/slide_catalog_numbers.png){height=2000px}

>>>>

![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](~/tentilla_morph/Organismal_paper/IOB-PostReview/raw_figures/SM1_SIMMAPtentilla-01.png)

@@

![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoband phenotype presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)

@@
